---
title: "Coronavirus misinformation beliefs"
author: "Daniel Allington"
date: "3/9/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)

library(dplyr)               # for tidy data manipulation
library(readr)               # for loading the data into memory
library(ggplot2)             # for tidy data visualisation

lul.d <- read_csv(
  '../data/life-under-lockdown-wave2-extract.csv',
  col_types = cols(
    col_number(),            # age is a numeric variable,
    col_factor(),            # gender is a categorical variable,
    col_factor(              # know_facebook is a categorical variable
      levels = c(            
        'Nothing at all',    # the possible values of 
        'Not very much',     # know_facebook are in 
        'A fair amount',     # exactly this order
        'A great deal'       # (important for an ordinal variable)
        ), 
      ordered = TRUE),       # know_facebook is in fact ordinal
    col_number()))           # beliefs is a numeric variable

```

# Visualise categorical variables
## Gender
```{r}
lul.d %>%
  ggplot(aes(x = gender)) +
  geom_bar() +
  ggtitle('Gender of respondents')
```

## Use of Facebook as a source of knowledge about coronavirus
```{r}
lul.d %>%
  ggplot(aes(x = know_facebook)) +
  geom_bar() +
  ggtitle('Please tell us how much of what you know about coronavirus,\nif anything, comes from Facebook')
```

# Visualise numeric variables
## Age
```{r}
lul.d %>%
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 5) +
  ggtitle('Age of respondents')
```

## Misinformation beliefs
```{r}
lul.d %>%
  ggplot(aes(x = beliefs)) +
  geom_histogram(binwidth = 1) +
  ggtitle('Number of misinformation beliefs about coronavirus')
```

How many of the following does each respondent consider 'true' (answer options: 'true', 'false', 'don't know'):

* Coronavirus was probably created in a laboratory					
* The symptoms that most people blame on coronavirus appear to be linked to 5G network radiation	
* There is no hard evidence that coronavirus really exists				
* The number of people reported as dying from coronavirus is being deliberately exaggerated by the authorities
* The current pandemic is part of a global effort to force everyone to be vaccinated whether they want to or not

# Distribution of numeric variables
## Age
```{r}
lul.d %>%
  summarise(n = n(), Mdn = median(age), M = mean(age), SD = sd(age))
```

## Misinformation beliefs
```{r}
lul.d %>%
  summarise(n = n(), Mdn = median(beliefs), M = mean(beliefs), SD = sd(beliefs))
```

# Analysis
## Misinformation beliefs by gender
```{r}
lul.d %>%
  group_by(gender) %>%
  summarise(n = n(), Mdn = median(beliefs), M = mean(beliefs), SD = sd(beliefs))
```

